---
title: "Using Pander and Stargazer for Nice Tables in Markdown"
author: "Brian"
date: "9 August 2015"
output: html_document
---

Illustration of using **pander** for creating nice tables. Allows a lot of control over the look of a table compared to say knitr::kable. Inspried by http://kbroman.org/knitr_knutshell/pages/figs_tables.html by Karlo Broman. There is also xtable but not investigated here. 

Also looked at is **stargazer**. stargazer is an R package that creates LATEX code, HTML code and ASCII text for well-formatted regression tables, with multiple models side-by-side, as well as for summary statistics tables, data
frames, vectors and matrices. (https://cran.r-project.org/web/packages/stargazer/vignettes/stargazer.pdf)

Other libraries include (apsrtable, xtable, texreg, memisc, outreg)

```{r,echo=FALSE}

#Matching phrase to meaning. 
terms<-c("Influential observation",
         "SSE","r-sq.",
         "Residual",
         "s",
         "High leverage point","r","SST","Outlier","SSR","Cooks distance")

defs<-c("An observation that alters the regression parameters significantly based on its prsence or absence in the data set.",
        "Represents an overall measure of the error in prediction resulting from the use of the estimated regression equation.",
        "The proportion of the variability in the response that is explained by the linear relationship betwen the predictor and response variables.",
        "The vertical distance between the repsonse predicted an the actual response.",
        "Measures the **typical** difference between the predicted and actual response values. - standarzied.",
        "An observation that is extreme in the predictor space (x-variables), without reference to the response variable.",
        "Measures the strength of the linear relationship between two quantitative variables, with values ranging form -1 to 1",
        "Represents the total variability in the values of the response variable  alone, without referecne to the predictor.",
        "An observation that has a very large standardized residual in absolute value.",
        "Measures the overall improvement in predictor accuracy when usingthe regression as opposed to ignoring the predictor information",
        "Measures the level of influence of an observation by taking into account both the size of the residual and the amount of leverage for that observation.") 
```

```{r,echo=FALSE}
df<-data.frame(Term=terms,Definition=defs)
df$Term<-as.character(df$Term) #go in as factors. 
df$Definition<-as.character(df$Definition) #go in as factors. 
df$test<-c(1,3,4,5,6,3,8,4,6,8,4)
temp<-sapply(df$Term, nchar)  #check legths of strings
```


```{r}
library(pander)

####
#Well, not using colors (as not supported by markdown), but you can highlight cells/rows/columns of the table with #pandoc.table and the general pander method by using bold or italics font face:
###

emphasize.rows(4) #Makes italic
emphasize.strong.cells(which(df == 8, arr.ind = TRUE))  #not sure how to pass a fucntion parameters? 
emphasize.strong.rows(which(nchar(df$Term) == 23))


#Cell alignment 
#nice way of specifiy alignment. 
panderOptions('table.alignment.default',function(df) ifelse(sapply(df, is.numeric), 'right', 'left')) 

#Override the above
panderOptions('table.alignment.default','left')
#Splitting cells and tables based on width. 
pander(df,caption="Matching", split.cells = c(10,60,5), split.tables =150)  #note it splits the code block on output. 

#pander is a wrapper on pandoc.table
#pander(pandoc.table(df, split.cells = c(10,60,5)))  


```

Now using stargazer and a linear regression. Will flesh out with other models as develos. 

```{r, echo=FALSE,include=FALSE}
mydata<-read.csv(file="data/baseball.csv")

#subset data
nrow(mydata) #331
nrow(mydata[mydata$at_bats>100,])  #209
sub_md<-mydata[mydata$at_bats>100,]  


#Create a scatter plot of "stolen_bases" vs. "caught_stealing"
library(ggplot2)
p1 <- ggplot(sub_md, aes(x = stolen_bases, y = caught_stealing))
p2<-p1+geom_point(aes(color = triples))
p3<-p2+ labs(x="Stolen Bases",y = "Caught Stealing")  
p3

#changes the position of the legend
l1<-p3+theme(legend.position=c(1,0),legend.justification=c(0.9,-0.1))   #not sure how legend position works, must check out
l1
```

Now onto the regression. Stargazer, taken from http://jakeruss.com/cheatsheets/stargazer.html

```{r,results="asis"}
fit1<-lm(caught_stealing~stolen_bases,data=sub_md)
fit2<-lm(caught_stealing~stolen_bases*walks,data=sub_md)

#Stargazer allows to look at the two models nicely. 
library(stargazer)
stargazer(fit1,type="html",style = "all")
stargazer(fit1,type="html",style = "all",title= "These are awesome results!")
stargazer(fit1,type="html",style = "all",ci=TRUE)
stargazer(fit1,fit2,type="html",style = "all",ci=TRUE)
#for with glm
#fit1 <- glm(F~x1+x2+x3,data=mydata,family=binomial())# not sure if it is possibles to this. 



```


